%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{academicons}
\input{glyphtounicode}

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\

    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Mahyar Riazati} \\ \vspace{8pt}
    \small
    \faEnvelope \hspace{.5pt} \href{mailto:mhyrzt@gmail.com}{mhyrzt@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/mhyrzt}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/mhyrzt}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://mhyrzt.me}{Webpage}
    $|$
    \faGraduationCap \hspace{.5pt} \href{https://scholar.google.com/citations?user=k-nwlcYAAAAJ&hl=en}{Scholar}
    $|$
    \faMapMarker \hspace{.5pt} Tehran, Iran
\end{center}

%----------- EDUCATION -----------

\section{Education}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeEducationHeading
{Tehran University}{Tehran, Iran}
{M.Sc. in Electrical Engineering - Telecommunication Systems; \textbf{GPA: 3.5/4.00}}{Sep 2022 \textbf{--} Jan 2024}
{} {}
\resumeSubHeadingListStart
\small{\item{\textbf{Thesis:} Under the supervision of \href{https://ece.ut.ac.ir/en/~mnili}{\color{blue}Dr.Majid Nili Ahmad Abadi}}}
\resumeSubHeadingListEnd

\resumeEducationHeading
{Islamic Azad University - South Tehran Branch}{Tehran, Iran}
{B.Sc. in Electrical and Telecommunication Engineering; \textbf{GPA: 3.103/4.00}}{Sep 2017 \textbf{--} Jan 2022}
{} {}
\resumeSubHeadingListStart
\small{\item{\textbf{Undergrad Project:} Face Landmark Detection for Android Devices Under the supervision of  \href{https://www.linkedin.com/in/sedigheh-ghofrani-b6495b63/}{\color{blue}Dr.Sedigheh Ghofrani}}}
\resumeSubHeadingListEnd

\resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
\vspace{2pt}
\resumeSubHeadingListStart
\small{\item{
                \textbf{AI:}{ scikit-learn, numpy, pandas, PyTorch, OpenCV, Image Processing, Fuzzy Logic, Reinforcement Learning} \\ \vspace{3pt}
                \textbf{EE:}{ Altium Designer, Arduino, AVR, ESP32, MATLAB, Simulink, DSP} \\ \vspace{3pt}
                \textbf{SE:}{ FP, OOP, TDD, C/C++, Python, Java, Android } \\ \vspace{3pt}
                \textbf{DB:}{ PostgreSQL, MySQL, MongoDB, MinioDB  } \\ \vspace{3pt}
                \textbf{Tools:}{ git, GNUMake, CMake, Docker, Unity  } \\ \vspace{3pt}
                \textbf{Back-End:}{ Flask, Django + DRF,  Node.JS, express, php } \\ \vspace{3pt}
                \textbf{Front-End:}{ HTML, CSS, SCSS, JS, TS, React/Next, Cypress, React Testing Library } \\ \vspace{3pt}
          }}
\resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Work Experience}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://quera.org/}{\color{blue}Quera}}{Tehran, Iran}
{Bootcamp Mentor and Instructor}{Jul 2022 \textbf{--} Nov 2022, Full-time}
\resumeItemListStart
\resumeItem{Assisted in planning, course component selection, and problem design for data science Bootcamp.}
\resumeItem{Instructor of Numpy, Pandas, SQL, Fundamental Concepts of Supervised and Unsupervised Learning and Artificial Neural Networks.}
\resumeItem{Responsible for Planning, course component selection, and problem design for a front-end development Bootcamp.}
\resumeItem{Taught WebAPIs, WebSockets, and React Router.}
\resumeItemListEnd
\resumeSubSubheading{Front-End College Section Chief}{Dec 2021 \textbf{--} Nov 2022, Full-Time}
\resumeItemListStart
\resumeItem{Maintained Two major courses on front-end development \& React.js with more than 3000 participants.}
\resumeItem{Revised technical contents of the course and the problems given to the participants based on the up-to-date needs of the tech industry, resulting in a 50\% increase in the NPS score of the front-end college.}
\resumeItemListEnd
\resumeSubSubheading{Programming Contest Designer}{Sep 2021 \textbf{--} Nov 2022, Full-Time}
\resumeItemListStart
\resumeItem{Responsible for planning and designing a programming recruitment contest on React.js for Mofid Securities for more than 1500 participants.}
\resumeItem{Advisor and technical assistant of DigiKala programming contests.}
\resumeItem{Developed an online judgment system for mobile app developments with React Native.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{Cognitive Systems Lab at Tehran University}{Tehran, Iran}
{Research Assistant}{May 2023 \textbf{--} Present, Full-time}
\resumeItemListStart
\resumeItem{Developing Bunch of stuffs}
\resumeItemListEnd

\resumeSubheading
{Artificial Creatures Lab at Sharif University of Technology}{Tehran, Iran}
{Research Assistant}{Mar 2022 \textbf{--} Apr 2024, Part-time}
\resumeItemListStart
\resumeItem{Collaborated within a dynamic research team led by \href{https://ee.sharif.edu/~bagheri-s/}{\color{blue}Dr.Saeed Bagheri Shouraki} to develop innovative algorithms aimed at expediting and enhancing the stability of training processes. Transformed the initial goal of finding a method into developing a sophisticated algorithm for transferring learned insights from one problem to another. Leveraged sidechannels data from expert agents to optimize and augment the efficiency of knowledge transfer mechanisms.}
\resumeItem{Organized the code written by the research group members and the results of experiments into a repository.}
\resumeItem{Developed various modules for Reinforcement Learning applications such as DQN to make the codebase more uniform and reliable.}
\resumeItem{Discovered a new method inspired by Ink Drop Spread (IDS) from fuzzy logic that led to a 50 percent optimization in the training process and increased the stability of the Q-Learning process.}
\resumeItem{Developed a customizable environment with Unity Engine and MLAgents.}
\resumeItem{Developed a pipeline with a simple and user-friendly interface to run the experiments faster and easier. (\href{https://github.com/alighandij/Ex-RL-virtual-lab}{\color{blue}GitHub})}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------- PUBLICATIONS -----------
\section{Publications}
\vspace{3pt}
\resumeItemListStart
\resumeItem{A. Ghandi, S. B. Shouraki, I. Gholampour, A. Kamranian, and \textbf{M. Riazati}, "Ex-RL: Experience-based reinforcement learning," \emph{Information Sciences}, vol. 689, p. 121479, 2025, doi: \href{https://doi.org/10.1016/j.ins.2024.121479}{\color{blue}10.1016/j.ins.2024.121479.}}

\resumeItem{A. Ghandi, S. B. Shouraki and \textbf{M. Riazati}, "Deep ExRL: Experience-Driven Deep Reinforcement Learning in Control Problems," \emph{2024 12th Iran Workshop on Communication and Information Theory (IWCIT)}, Tehran, Iran, Islamic Republic of, 2024, pp. 1-6, doi: \href{https://doi.org/10.1109/IWCIT62550.2024.10552959}{\color{blue}10.1109/IWCIT62550.2024.10552959.}}
\resumeItemListEnd

%----------- AWARDS & ACHIEVEMENTS -----------

% \section{Awards \& Achievements}
% \vspace{2pt}
% \resumeSubHeadingListStart
% \small{\item{
% \textbf{High Honors Degree:}{ Awarded to Bachelor alumni who have graduated with a GPA greater than or equal to 3.50 by Boğaziçi University. (Jul 2023)} \\ \vspace{3pt}

% \textbf{TÜBİTAK 2247-C Intern Researcher Scholarship:}{ Awarded to undergraduate students who take part in research projects carried out by the Scientific and Technological Research Council of Turkey (TÜBİTAK). (Dec 2021 \textbf{--} Jun 2022)} \\ \vspace{3pt}

% \textbf{National University Admission Exam (YKS):}{ Ranked $75^{th}$ in Mathematics and Science among ca. 2.3 million candidates with a test score of 489.92/500. (Jul 2018)} \\ \vspace{3pt}

% \textbf{KYK Outstanding Success Scholarship:}{ Awarded to undergraduate students who have been ranked in the top 100 on National University Admission Exam by Higher Education Credit and Hostels Institution (KYK). (Sep 2018 \textbf{--} Jun 2023)} \\ \vspace{3pt}

% \textbf{Boğaziçi University Success Scholarship:}{ Awarded to undergraduate students who have been ranked in the top 100 on National University Admission Exam by Boğaziçi University. (Sep 2018 \textbf{--} Jun 2023)} \\ \vspace{3pt}

% \textbf{Duolingo English Test (DET):}{ Overall Score: 135/160} \\ \vspace{3pt}

% \textbf{Boğaziçi University English Proficiency Test (BUEPT):}{ Achieved the highest grade A on the BUEPT grading scheme with a total score in the range of 85-100.} \\ \vspace{3pt}

% \textbf{Kocaeli Science High School Salutatorian Award:}{ Graduated as the second-highest ranked student in my class.}
% }}
% \resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{Projects}
\vspace{3pt}
\resumeSubHeadingListStart




\resumeProjectHeading
{\textbf{DLIB Android Face Landmark Detection} $|$ \emph{\href{https://github.com/mhyrzt/Dlib-Android-Face-Landmark}{\color{blue}GitHub}}}{}
\resumeItemListStart
\resumeItem{Spearheaded my final undergraduate project under the guidance of \href{https://www.linkedin.com/in/sedigheh-ghofrani-b6495b63/}{\color{blue}Dr. Sedigheh Ghofrani}, dedicated to implementing face landmark detection on Android devices.}
\resumeItem{Leveraged Java to craft the user interface and implement critical functionalities.}
\resumeItem{Employed the OpenCV Java Library for proficient image processing and editing.}
\resumeItem{Seamlessly integrated the dlib library, crafted in C++, by harnessing the NDK within the Java framework. Utilized C++ and CMake to enable 68-point face landmark detection on Android devices.}
\resumeItemListEnd





\resumeProjectHeading
{\textbf{Simple Multi Agent Deep Reinforcement Learning Chess} $|$ \emph{\href{https://github.com/mhyrzt/Simple-MADRL-Chess}{\color{blue}GitHub}}}{}
\resumeItemListStart
\resumeItem{Developed a chess environment using Pygame for a fun holiday project.}
\resumeItem{Applied the Proximal Policy Optimization (PPO) algorithm to solve the chess environment, excluding en passant and castling moves.}
\resumeItem{Trained two agents with separate neural networks, engaging in self-play to enhance their gameplay.}
\resumeItem{Trained a single agent with a singular neural network, capable of playing both white and black pieces through joint training.}
\resumeItemListEnd


\resumeProjectHeading
{
    \textbf{Koch Snowflake}
    $|$ \emph{\href{https://github.com/mhyrzt/KochSnowFlake}{\color{blue}GitHub}}
    $|$ \emph{\href{https://mhyrzt.github.io/KochSnowFlake/}{\color{blue}Website}}
}
{}
\resumeItemListStart
\resumeItem{Developed an interactive web application using React and TypeScript for generating Koch snowflakes, a visually intricate fractal pattern.}
\resumeItem{Implemented a dynamic user interface allowing real-time adjustments to parameters such as iteration levels and line lengths, providing an engaging user experience.}
\resumeItem{Translated the recursive Koch snowflake algorithm into efficient TypeScript code, striking a balance between performance and readability.}
\resumeItemListEnd

\resumeProjectHeading
{
    \textbf{Elementary Cellular Automaton}
    $|$ \emph{\href{https://github.com/mhyrzt/elementary-cellular-automaton}{\color{blue}GitHub}}
    $|$ \emph{\href{https://mhyrzt.github.io/elementary-cellular-automaton/}{\color{blue}Website}}
}
{}
\resumeItemListStart
\resumeItem{A React.js Project enabling the generation of \href{https://en.wikipedia.org/wiki/Elementary_cellular_automaton}{\color{blue} Elementary Cellular Automataton} with various rules and sizes. }
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Unity MountainCar 2D} $|$ \emph{\href{https://github.com/mhyrzt/UnityMountainCar2D}{\color{blue}GitHub}}}{}
\resumeItemListStart
\resumeItem{Developed Unity Mountain Car 2D as part of my research assistant role in Artificial Creature Labs.}
\resumeItem{Crafting a 2D version of the Mountain Car problem within the Unity framework.}
\resumeItem{Utilizing Unity ML-Agents Toolkit to enable reinforcement learning in the 2D environment.}
\resumeItem{Providing flexibility by allowing adjustments to the position of the goal, adding height offsets, changing gravity, and fine-tuning car properties such as mass and force.}
\resumeItemListEnd


\resumeProjectHeading
{\textbf{PrecoderNet} $|$ \emph{\href{https://github.com/mhyrzt/PrecoderNet}{\color{blue}GitHub}}}{}
\resumeItemListStart
\resumeItem{Implemented "PrecoderNet: Hybrid Beamforming for Millimeter Wave Systems with Deep Reinforcement Learning" paper using a DDPG model.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{ALOHASIM} $|$ \emph{\href{https://github.com/mhyrzt/ALOHASIM}{\color{blue}GitHub}}}{}
\resumeItemListStart
\resumeItem{Conducted a comprehensive simulation of the ALOHA Protocol as a key component of a Telecommunication Undergraduate course project.}
\resumeItem{Implemented a dynamic visualization of node interactions using the pygame framework, providing a clear and engaging representation of the protocol's functioning.}
\resumeItemListEnd


\resumeSubHeadingListEnd

%----------- RELEVANT COURSEWORK -----------

\section{Relevant Coursework}
\vspace{2pt}
\resumeSubHeadingListStart
\small{\item{
                \textbf{M.Sc. coursework:}{ Stochastic Processes, Advance Digital Signal Processing, Convex Optimization, Machine Learning, Reinforcement Learning, Foundational Models in NLP, Advance Telecommunication Theory} \\ \vspace{3pt}
                \textbf{B.Sc. coursework:}{ Electrical Circuits I-II, Probability Theory, Electronics I-II, Signals and Systems, Digital System Design I-II, Electromagnetic, Fields \& Waves, Microwave, Antenna, Linear Control, Principals of Communication Systems, Digital Signal Processing, Digital Communications, Telecommunication Networks } \\ \vspace{3pt}
          }}
\resumeSubHeadingListEnd

%----------- CERTIFICATES -----------

\section{Certificates}
\resumeSubHeadingListStart

\resumeOrganizationHeading
{Reinforcement Learning Specialization}{Jun 2021}{\href{https://coursera.org/share/38a7e63a9ebdbc73df6e85bcc6e10280}{\color{blue} Coursera \textbf{--} University of Alberta}}

\resumeOrganizationHeading
{Generative Adversarial Networks Specialization}{Jun 2021}{\href{https://coursera.org/share/f9336c54f7b154755888c616512824b8}{\color{blue} Coursera \textbf{--} DeepLearning.ai}}

\resumeOrganizationHeading
{Mathematics for Machine Learning: Linear Algebra}{Apr 2021}{\href{https://www.coursera.org/account/accomplishments/certificate/4Q3SNCJBQQ2D}{\color{blue}Coursera \textbf{--} Imperial College London}}

\resumeOrganizationHeading
{Deep Learning Specialization}{Mar 2021}{\href{https://www.coursera.org/account/accomplishments/specialization/certificate/ZVSQTA78X4DK}{\color{blue} Coursera \textbf{--} DeepLearning.ai}}

\resumeOrganizationHeading
{Proffessional Project-Oriented Course in Backend Development with Django} {Oct 2020}
{\href{https://quera.org/certificate/LcnssaOX/}{\color{blue}Quera}}

\resumeOrganizationHeading
{Advance Algorithmic Thinking and Data structure} {Oct 2020}
{\href{https://quera.org/certificate/TutKPvCg/}{\color{blue}Quera}}

\resumeOrganizationHeading
{Project-Oriented Course in Web Development with PHP} {May 2020}
{\href{https://quera.org/certificate/Au1OnMWM/}{\color{blue}Quera}}

\resumeOrganizationHeading
{Advance Python Programming and Object-Oriented Thinking Course} {May 2020}
{\href{https://quera.org/certificate/Au1OnMWM/}{\color{blue}Quera}}

\resumeSubHeadingListEnd

%----------- ORGANIZATIONS -----------

% \section{Organizations}
% \resumeSubHeadingListStart

% \resumeOrganizationHeading
% {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}

% \resumeSubHeadingListEnd

%----------- HOBBIES -----------

% \section{Hobbies}
% \resumeSubHeadingListStart
% \small{\item{Anime, Manga, Video Games, Cafe, YouTube, Learning new Stuffs}}
% \resumeSubHeadingListEnd

%----------- REFERENCES -----------

\section{References}
\vspace{2pt}
\resumeSubHeadingListStart
\item{References available upon request.}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
